### 2025-04-24 conteudo/background/linux.tex
remove TODO's
add comments on todos for the dissertation text

\todo[inline]{Adicionar um "preambulo" antes da seções do capítulo}

@@

\todo[inline]{FIND MAILING LIST AND CITE HERE (DONE?) }

>>>>

@@

\todo[inline]{Require an introduction about IIO drivers.}

\todo[inline]{Not exactly on this section, but I need to mention GIT, as one of the similarity methods is based on the GIT command.}

### 2025-04-24 conteudo/background/refactor.tex
add comments on todos for the dissertation text

Fowler defines refactoring in his book as "a controlled technique for improving the design of an existing code base. 
Its essence is applying a series of small behavior-preserving transformations, each of which is too small to be worth 
doing. However, the cumulative effect of each of these transformations is quite significant." \citep{refactorbook}. 
The elimination of detected code clone duplication is a refactoring task that necessitates the 
application of refactoring methods. Fowler presents multiple refactoring methods such as the 
\textit{parameterize method}, the \textit{replace parameter with explicit methods} and 
the \textit{replace parameter with method} \citep{refactorbook}. 
There is a brief explanation of the methods used in our research below.

\subsection{Parameterize method}

TODO. I EXPECT TO FILL THIS SECTION AS THE WORK EVOLVES.

>>>>

\todo[inline]{Reconsider if I need this function anymore.}

Fowler defines refactoring as "a controlled technique for improving the design
of an existing code base. Its essence is applying a series of small
behavior-preserving transformations, each of which is too small to be worth
doing. However, the cumulative effect of each of these transformations is quite
significant" \citep{refactorbook}. The elimination of detected code clones and
duplication is a refactoring task that requires the application of refactoring
methods. Fowler presents several refactoring techniques, including
\textit{parameterize method}, \textit{replace parameter with explicit methods},
and \textit{replace parameter with method} \citep{refactorbook}. Below is a
brief explanation of the methods used in our research.

\begin{figure}[ht]
\includegraphics[scale=0.36]{refactor/parameterize}
\caption{Example of Parameterize Method usage.}
\label{fig:parameter}
\end{figure}

\begin{figure}[ht]
\includegraphics[scale=0.36]{refactor/extract}
\caption{Example of Extract Method usage.}
\label{fig:extract}
\end{figure}

\paragraph{Parameterize Method.}

The Parameterize Method involves replacing multiple similar code blocks with a
single function. This function incorporates parameters to account for the
different behaviors across similar code snippets, allowing it to adjust
functionality based on the parameter values \citep{refactorbook}. Figure
\ref{fig:parameter} illustrates an example of the Parameterize Method.

\paragraph{Extract Method.}

The Extract Method entails breaking down a complex code artifact into multiple,
simpler methods or functions. One of the primary advantages of this method is
that the newly created functions can be reused throughout the project. By
contrast, a complex code artifact might not be entirely reusable, potentially
resulting in further code duplication \citep{refactorbook}. Figure
\ref{fig:extract} demonstrates an example of the Extract Method.

### 2025-04-24 conteudo/eval/eval.tex
add comments on todos for the dissertation text

>>>>

\todo[inline]{As it is primarly results, everything should be remade, the structure of the files for this section is bad.}

\todo[inline]{Remember the typos on the tables. }

\todo[inline]{Idea: The research methods should be 3 phases, one of the tool creation/testing, one for the my experiences submiting a path, and the last for the experiences of the students on the course. Maybe split in four to split the tool creation for the tool testing.}

### 2025-04-24 conteudo/methods/methods.tex
add comments on todos for the dissertation text

@@

@@

@@

>>>>

\todo[inline]{The focus of the above section should be a little more on the tool, the introduction about mitigating duplications is good enough. A little about the fact that we will test on IIO later maybe is good. }

\todo[inline]{I SHOULD mention that the test on the tool were made using the gensim similarity method and not the git method.}

@@

\todo[inline]{I just mention the problem, maybe a more explictly mention of the problem here or on the background would be good.}

@@

\todo[inline]{Take care: Big focus on AMD display driver and the tone of the writing supports the focus. }

@@

\todo[inline]{THE WHOLE SECTION NEEDS TO BE REMADE.}

### 2025-04-24 conteudo/tool/tool.tex
add comments on todos for the dissertation text

>>>>

\todo[inline]{I need to rename the Setup as Preprocessor step.}

\todo[inline]{Update the Function parser description of the C parser and Java parser}

\todo[inline]{Add the other similarity method added on the tool using git for the Code Duplication Finder.}

\todo[inline]{Update diagram and functionalites pictures (do not need sudo anymore!).}

\todo[inline]{Big maybes: Describe more how the functionalites are implemented, as the focus shifted for the tool as of now.}
